From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-13 Article.Rmd
1

---
title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
author: 
  - name          : "Tanase Tasențe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "tanase.tasente@365.univ-ovidius.ro"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Equal contribution"
      - "Conceptualization"
      - "Data curation"
      - "Investigation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2"
    role:
      - "Equal contribution"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Data curation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
  - name          : "Cristina Dana Popescu"
    affiliation   : "1"
    role:
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Professional proofreading"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania"
  - id            : "2"
    institution   : "University of Bucharest, Romania"
authornote: |
  Department of Administrative and Social Sciences
abstract: |
 This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform digital governance environment.

keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount         : "4067 words in text body 1034 words in reference section"
bibliography      : ["r-references.bib", "references.bib"]
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
documentclass     : "apa7"
classoption       : "man"
csl               : apa.csl
output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_docx
header-includes:
  - \usepackage{ragged2e}
---

>>>>

---
title: 'From Likes to Change: Assessing the Impact of Citizen Engagement on the European
  Commission''s Social Media Platforms'
author:
- name: Tanase Tasențe
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: "tanase.tasente@365.univ-ovidius.ro"
  role:
  - Equal contribution
  - Conceptualization
  - Data curation
  - Investigation
  - Formal analysis
  - Resources
  - Software
  - Visualization
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
- name: "Cristian Opariuc-Dan"
  affiliation: '1,2'
  role:
  - Equal contribution
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
  - Data curation
  - Formal analysis
  - Resources
  - Software
  - Visualization
- name: Cristina Dana Popescu
  affiliation: '1'
  role:
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
  - Professional proofreading
shorttitle: Impact of Citizen Engagement on the European Commission's Social Media
  Platforms
output:
  html_document:
    df_print: paged
  word_document: papaja::apa6_docx
  pdf_document: papaja::apa6_pdf
authornote: |
  Department of Administrative and Social Sciences
abstract: "This study investigates the role of emotional resonance in social media
  communications from the European Commission (EC) and its impact on public participation
  across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings
  indicate that emotionally resonant communications significantly enhance public engagement,
  with variations depending on the specific platform. Both positive and negative emotional
  resonance significantly impact participation, with the latter having a more pronounced
  effect. Our research highlights the critical importance of platform-specific strategies
  and the incorporation of emotional resonance in public communications to foster
  participation in policy dialogues. An analysis of the engagement rates and sentiment
  across platforms reveals unique tonal variations in the EC's discourse. The effect
  of emotional resonance on public engagement is also found to be moderated by the
  choice of social media platform, with certain platforms more significantly moderating
  the relationship between emotional resonance and engagement than others. This study
  lays the groundwork for refining communication strategies within a multi-platform
  digital governance environment.\n"
keywords: "social media, public institutions, emotional resonance, public engagement,
  platform-specific strategies, digital governance"
wordcount: 4067 words in text body 1034 words in reference section
bibliography:
- "r-references.bib"
- references.bib
floatsintext: no
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: man
csl: apa.csl
affiliation:
- id: '1'
  institution: Ovidius University of Constanța, Romania
- id: '2'
  institution: University of Bucharest, Romania
header-includes: \usepackage{ragged2e}
---
